### 2017-12-27 icde/revision/Response.tex

Dear Reviewers,

This is the response letter regarding the revised version of our submission to IEEE International Conference on Data Engineering 2018, \emph{Query Independent Scholarly Article Ranking}.

We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.

The paper has been substantially revised according to the referees¡¯ comments. In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing, (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our technique with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.

@@

%******************* reviewer 1 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 1.}

\textbf{[R1W1]} \emph{Formula 7 in SARank still needs parameters, which are not easy to set.}

We discuss the necessity and the selection of parameters right after Eq. (7) (left column, page 4). More specifically, these parameters enable our model to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters. As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (please also refer to our analysis in Exp-4.3).

@@

%The parameters are designed to fit variety ranking with different demands. For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component. Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.

\textbf{[R1W2]} \emph{The extension of this method to query dependent ranking or other heterogeneous information network should be discussed.}

We discuss the extension of query dependent ranking in the revised paper (left column, page 2).
%
This work focuses on query independent ranking because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search.
And our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
%
The extension in other heterogeneous information networks is currently unclear, since the TWPageRank is derived from an analysis of impacts of articles (left column, page 2). We shall identify possible applications in the future.

@@

We clarify the reasons of not changing values on nodes at the revised version (Remarks, left column, page 3).
The goal of our TWPageRank is to change node values, \ie importance.
%One may wonder why not directly change node values.
Directly changing node values, however, is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it. Finally, we use impact weights to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.

\textbf{[R1D2]} \emph{This paper has an important observation that ¡°the impact of an article tends to decay with time after the peak time only.¡± However, I cannot see that from Figure 1. It is better to add some references to support the claim.}

Figure 1 shows the logscale percentage of the number of articles/citations of each year which grows exponentially with time, instead of numbers of citations (\ie impacts) of individual articles.
We have highlighted it in the revised version (Figure 1, page 2).

We have explained our claim better. The observation is inspired by the five distinct citation patterns. Considering that the direct decay model only conforms with {\em MonDec}, we thus propose our claim that can better explain the five citation patterns. Moreover, reference [17] exploits a log-normal survival probability which also decays with time after the citation peak.
%(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).

[17]  D. Wang, C. Song, and A. Barab¨¢si, ¡°Quantifying long-term scientific impact,¡± Science, vol. 342, no. 6154, pp. 127-132, 2013.

@@

\textbf{[R1D3]} \emph{How to determine the peak time for the PeakMul pattern?}

The PeakMul pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years. In our work, we unify the five patterns and only use the latest peak time which we have discussed in Section II-A (para 1, left column, page 3).

[18]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.

@@

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

\marked{Yes, we have gone over the paper and improved the presentation to make it more understandable. }
%Thanks for the suggestion!

\textbf{[R2D1]} \emph{There seem to be two ``contradictory" sides to this paper. From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We thank the reviewer for appreciating the practice merit of our work which is drawn from an important and practical problem.
%
And we believe this paper also stands from research and technique perspective.
%
The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions. Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on a impractical assumption that there is no citations between articles of the same years.
%
Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly graphs which has its own unique features.  To conclude, we are not simply applying existing techniques into a different domain.
%
We have further clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.
%
Please also refer to our response to R2W1.

[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.

### 2017-12-27 icde/revision/sec-alg.tex

\begin{proofSketch}
We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes computed earlier. %(see~\cite {ERank-full} for details). % since $\epsilon > ||PR^+-PR||_1 = ||d\cdot M^T \cdot (PR-PR^*)||_1 + ||PR-PR^*||_1$.
\end{proofSketch}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5 &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

\stitle{Time \& space complexity analyses of the batch algorithm}.
%
By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships, and takes $O(7|V^c|+2|V^c{'}|+4|V^v|+2|V^v{'}|+|E^c|+|E^c{'}|+|E^v|+|E^v{'}|+2|A|+|D|)$ space, where $|A|$ is the number of authors and $|D|$ is the size of academic graph data $D$.
% TWPageRank on V^c: 3|V^c| + |E^c| + 2|V^c{'}| + |E^c{'}|
% TWPageRank on V^v: 3|V^v| + |E^v| + 2|V^v{'}| + |E^v{'}|
% Prestige of authors: |A|
% popularity: |V^c| + |V^v| + |A|
% Importance scores: 3|V^c|
% D: academic graph data, i.e., |PA|, |PV|, paper years, ect
% total: 7|V^c| + |E^c| + 2|V^c{'}| + |E^c{'}| + 4|V^v| + |E^v| + 2|V^v{'}| + |E^v{'}| + 2|A| + |D|

The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc uses $(2|V^c{'}|+|E^c{'}|)$ and $(2|V^v{'}|+|E^v{'}|)$ extra space to store the block-wise graphs $G^c{'}(V^c{'},E^c{'})$ of $G^c$ and $G^v{'}(V^v{'},E^v{'})$ of $G^v$ and their topological orders, while speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$.

>>>>

\eat{
\begin{proofSketch}
We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes computed earlier. %(see~\cite {ERank-full} for details). % since $\epsilon > ||PR^+-PR||_1 = ||d\cdot M^T \cdot (PR-PR^*)||_1 + ||PR-PR^*||_1$.
\end{proofSketch}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
%\begin{small}
%\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5K &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

@@

\eat{   %% time & space complexity
\stitle{Time \& space complexity analyses of the batch algorithm}.
%
By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships, and takes $O(7|V^c|+2|V^c{'}|+4|V^v|+2|V^v{'}|+|E^c|+|E^c{'}|+|E^v|+|E^v{'}|+2|A|+|D|)$ space, where $|A|$ is the number of authors and $|D|$ is the size of academic graph data $D$.
% TWPageRank on V^c: 3|V^c| + |E^c| + 2|V^c{'}| + |E^c{'}|
% TWPageRank on V^v: 3|V^v| + |E^v| + 2|V^v{'}| + |E^v{'}|
% Prestige of authors: |A|
% popularity: |V^c| + |V^v| + |A|
% Importance scores: 3|V^c|
% D: academic graph data, i.e., |PA|, |PV|, paper years, ect
% total: 7|V^c| + |E^c| + 2|V^c{'}| + |E^c{'}| + 4|V^v| + |E^v| + 2|V^v{'}| + |E^v{'}| + 2|A| + |D|

The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc uses $(2|V^c{'}|+|E^c{'}|)$ and $(2|V^v{'}|+|E^v{'}|)$ extra space to store the block-wise graphs $G^c{'}(V^c{'},E^c{'})$ of $G^c$ and $G^v{'}(V^v{'},E^v{'})$ of $G^v$ and their topological orders, while speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$.
}  %%% eat

\stitle{Time complexity analysis of the batch algorithm}.
%
By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships.
%
The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$ at an extra space cost for the block-wise graphs of $G^c$ and $G^v$ and their topological orders.
